---
title: "'Variability in meta-analysis estimates of continuous outcomes using different standardization and scale-specific re-expression methods: R code"
author: "Gallardo-Gómez, D."
date: '2023-09-27'
output: html_document
---


Load the required libraries

```{r, message=FALSE, warning=FALSE, error=FALSE, results='hide'}
library(tidyverse)
library(tidybayes)
library(brms)
library(readxl)
library(ggthemes)
library(ggsci)
library(cowplot)
library(MBNMAdose)
library(kableExtra)
library(ggdist)
library(patchwork)
library(ggmcmc)
library(ggridges)
library(modelr)
library(marginaleffects)
library(glue)
library(ggpubr)
```

```{r}
# Function to compute Deviance Information Criteria [DIC] parameters
dic_brmsfit <- function(object) {
  Dbar <- -2 * mean(rowSums(log_lik(object)))
  coef_pmean <- unname(fixef(object)[ , "Estimate"])
  res <- residuals(object)[ , "Estimate"]
  N <- length(res)
  sigma <- posterior_summary(object, variable = "sigma")[ , "Estimate"]
  Dhat <- -2 * sum(dnorm(res, sd = sigma, log = TRUE))
  p <- Dbar - Dhat
  elpd <- Dhat / -2 - p
  data.frame(elpd_dic = elpd, p_dic = p, dic = Dhat + 2 * p, 
             row.names = "Estimate")
}
```


Load our dataset and check it.

```{r, echo=FALSE}
data <- read_xlsx(path = "", # fill with the path where you save the dataset in Excel format
                  col_names = TRUE, na = "NA", sheet = "multinma")

# we should change the direction of the effect measures that indicated an outcome improvement with a mean reduction post-value
data <- data %>%
  mutate(y_int = ifelse(lower_better == "yes", y_int * -1, y_int),
         y_ext = ifelse(lower_better == "yes", y_ext * -1, y_ext))

# outcomes view
data %>%
  group_by(measure) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

# view our dataset
glimpse(data)
```


We are going to subset our dataset to create different databases referring each one to a specific outcome of interest. For the subsequent analysis, we're going to select the Short Physical Performance Battery (`SPPB`), which basically assesses the physical capacity of the patient, and the Barthel Index (`BI`), which measures the ability to carry out the activities of daily-living.

```{r}
# SPPB data
sppb_data <- data %>%
  filter(measure == "SPPB" & !diff == is.na(diff)) %>%
  mutate(class = factor(class, levels = c("Usual care",
                                          "Physical activity")))

# BI data
bi_data <- data %>%
  filter(measure == "BI" & !diff == is.na(diff)) %>%
  mutate(class = factor(class, levels = c("Usual care",
                                          "Physical activity")))


# inspecting the range of SD values
data.frame(scale = c("SPPB", "BI"),
           n_studies = c(nrow(sppb_data), nrow(bi_data)),
           pre_SD = c(paste("From", round(range(sppb_data$pre_sd_pooled)[1], 2), "to", round(range(sppb_data$pre_sd_pooled)[2], 2)), paste("From", round(range(bi_data$pre_sd_pooled)[1], 2), "to", round(range(bi_data$pre_sd_pooled)[2]))),
           post_SD = c(paste("From", round(range(sppb_data$post_sd_pooled)[1], 2), "to", round(range(sppb_data$post_sd_pooled)[2], 2)), paste("From", round(range(bi_data$post_sd_pooled)[1], 2), "to", round(range(bi_data$post_sd_pooled)[2]))),
           internal_SD = c(mean(sppb_data$pre_sd_pooled), mean(bi_data$pre_sd_pooled))) %>%
  mutate_if(is.numeric, round, 2)
```
  
  
## Fitting our meta-analysis models 

The main objective of this work is to compare how different standardization methods could impact in the posterior distribution of some important meta-analytic parameters such as the between-study heterogeneity, pooled mean difference, and posterior expectation of individual studies effects.

To transform back the standardised mean differences, we specify the SD references that we used.

```{r}
# external SD reference used for standardization
sppb_external_sd <- 3.14

# internal SD reference used for standardization
sppb_internal_sd <- sum(sppb_data$pre_sd_pooled) / nrow(sppb_data)

# internal SD reference used for standardization
sppb_internal_sd_post <- sum(sppb_data$post_sd_pooled) / nrow(sppb_data)

## weighted internal SD reference
sppb_weighted_ref <- 2.484051
```



### Prior distributions specification

```{r}
# naive prior information
vague_priors <- c(prior(normal(0, 100), class = Intercept),
                  prior(normal(0, 10), class = sd)) # 95% of the prior density lies between 0 and 19.6
```


#### Bit of data wrangling

```{r}
sppb_data <- sppb_data %>%
               mutate(studyID = case_when(
                 studyID == "Martinez-Velilla, 2019" ~ "Martinez-Velilla1",
                 studyID == "Martinez-Velilla, 2021" ~ "Martinez-Velilla2",
                 studyID == "Martinez-Velilla, 2022" ~ "Martinez-Velilla3",
                 studyID == "Campo, 2019" ~ "Campo, 2019",
                 studyID == "Kitzman, 2021" ~ "Kitzman, 2021",
                 studyID == "Ortiz-Alonso, 2020" ~ "Ortiz-Alonso, 2020",
                 studyID == "Casas-Herrero, 2022" ~ "Casas-Herrero, 2022"
               ),
               diff_w = diff / sppb_weighted_ref,
         se_diff_w = se_diff / sppb_weighted_ref)
```


### Fitting the models

```{r, results='hide', message=FALSE, warning=FALSE, error=FALSE}
# for reproducibility sake
set.seed(28032023)

# multilevel random-intercept meta-analysis using MD 
model <- brm(diff | se(se_diff, sigma = TRUE) ~ 1 + (1 | studyID),
             data = sppb_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-analysis using SMDs rescaled using an external SD reference 
model_ext <- brm(diff_ext | se(se_diff_ext, sigma = TRUE) ~ 1 + (1 | studyID),
             data = sppb_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-analysis using SMDs rescaled using an internal SD reference 
model_int <- brm(diff_int | se(se_diff_int, sigma = TRUE) ~ 1 + (1 | studyID),
             data = sppb_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-analysis using SMDs rescaled using the pooled SD of each study
model_pre <- brm(diff_pre | se(se_diff_pre, sigma = TRUE) ~ 1 + (1 | studyID),
             data = sppb_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-analysis using SMDs rescaled using the pooled SD of each study
model_post <- brm(diff_post | se(se_diff_post, sigma = TRUE) ~ 1 + (1 | studyID),
             data = sppb_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-anlaysis using SMDs rescaled using the weighted internal SD reference
model_w <- brm(diff_w | se(se_diff_w, sigma = TRUE) ~ 1 + (1 | studyID),
             data = sppb_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

```


### Model fit comparison

```{r}
# model fit comparison by DIC parameter
dic_brmsfit(model) %>% 
  rbind(dic_brmsfit(model_ext)) %>%
  rbind(dic_brmsfit(model_int)) %>%
  rbind(dic_brmsfit(model_pre)) %>%
  rbind(dic_brmsfit(model_post)) %>%
  as_tibble() %>%
  mutate(model = c("MD",
                   "External SD",
                   "Internal SD",
                   "Pre pooled study-specific SD",
                   "Post pooled study-specific SD")) %>%
  select(model, dic) %>%
  arrange(dic)
```


#### Convergence analysis

First, let's check if our model reached the convergence. We first check the mixing of the Markov Chain Monte-Carlo simulations, and we then observe the Potential Scale Reduction Factor ($\hat{R}$ parameter) which should be smaller than 1.05.

```{r}
# good mixing of our predictive chains
plot(model)

# posterior predictive check
pp_plot <- pp_check(model, ndraws = 50)
pp_plot.1 <- pp_check(model_pre, ndraws = 50)
pp_plot.2 <- pp_check(model_post, ndraws = 50)
pp_plot.3 <- pp_check(model_int, ndraws = 50)
pp_plot.4 <- pp_check(model_ext, ndraws = 50)

# observed Rhat value below 1.05
summary(model)
```


### SMD estimates and back transformation using corresponding SDs

In practice, people use the corresponding SD for standardization to unstandardize the pooled SMD estimate into scale-specific unit.

```{r}
# extract the posterior draws of the models
## observed mean differences
draws <- posterior_samples(model, c("^b", "^sd")) %>%
  mutate(type = "Pooled MD")

## mean differences rescaled using an external SD reference
draws_ext <- posterior_samples(model_ext, c("^b", "^sd")) %>%
  mutate(type = "External SD")

## mean differences rescaled using an internal SD reference
draws_int <- posterior_samples(model_int, c("^b", "^sd")) %>%
  mutate(type = "Internal SD")

## mean differences rescaled using the pooled SD of each study
draws_pre <- posterior_samples(model_pre, c("^b", "^sd")) %>%
  mutate(type = "Study-specific pooled SD\n(at pre-intervention)")

## mean differences rescaled using the pooled SD of each study
draws_post <- posterior_samples(model_post, c("^b", "^sd")) %>%
  mutate(type = "Study-specific pooled SD\n(at post-intervention)")

## mean differences rescaled using the weighted internal SD reference
draws.w <- posterior_samples(model_w, c("^b", "^sd")) %>%
  mutate(type = "Weighted internal SD")


# change the variables' names for simplicity sake
names(draws) <- c("intercept", "tau", "type")

names(draws_ext) <- c("intercept", "tau", "type")

names(draws_int) <- c("intercept", "tau", "type")

names(draws_pre) <- c("intercept", "tau", "type")

names(draws_post) <- c("intercept", "tau", "type")

names(draws.w) <- c("intercept", "tau", "type")


# unified dataset with all posterior iterations of the meta-analysis models
smd_data.final <- # draws %>%
  # mutate(intercept = 0, 
         # tau = 0) %>%
  rbind(draws_ext) %>%
  rbind(draws_int) %>%
  rbind(draws_pre) %>%
  rbind(draws_post)
  

# unified dataset with all data rescaled using each the corresponding reference SD values
md_data_final <- draws %>%
  rbind(draws_ext %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_int %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_pre %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_post %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) 


# numerical data
numerical.data.smd.final <- # fixef(model) %>%
  rbind(fixef(model_ext)) %>%
  rbind(fixef(model_int)) %>%
  rbind(fixef(model_pre)) %>%
  rbind(fixef(model_post)) %>%
  as_tibble() %>%
  mutate(type = factor(c("External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                         "Study-specific pooled SD\n(at post-intervention)"))) %>%
  # mutate(Estimate = ifelse(type == "Pooled MD", NA, Estimate)) %>%
  # mutate(Q2.5 = ifelse(type == "Pooled MD", NA, Q2.5)) %>%
  # mutate(Q97.5 = ifelse(type == "Pooled MD", NA, Q97.5)) %>%
  mutate_if(is.numeric, round, 2)

# tau estimates
posterior_summary(model_post)[2, ] * sppb_external_sd

# numerical MD data
numerical.data.final <- fixef(model) %>%
  rbind(fixef(model_ext)) %>%
  rbind(fixef(model_int)) %>%
  rbind(fixef(model_pre)) %>%
  rbind(fixef(model_post)) %>%
  as_tibble() %>%
  mutate(type = factor(c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                         "Study-specific pooled SD\n(at post-intervention)"))) %>%
  mutate(Estimate = case_when(
    type == "Pooled MD" ~ Estimate,
    type == "External SD" ~ Estimate * sppb_external_sd,
    type == "Internal SD" ~ Estimate * sppb_external_sd,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Estimate * sppb_external_sd,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Estimate * sppb_external_sd
  )) %>%
  mutate(Q2.5 = case_when(
    type == "Pooled MD" ~ Q2.5,
    type == "External SD" ~ Q2.5 * sppb_external_sd,
    type == "Internal SD" ~ Q2.5 * sppb_external_sd,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Q2.5 * sppb_external_sd,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Q2.5 * sppb_external_sd
  )) %>%
  mutate(Q97.5 = case_when(
    type == "Pooled MD" ~ Q97.5,
    type == "External SD" ~ Q97.5 * sppb_external_sd,
    type == "Internal SD" ~ Q97.5 * sppb_external_sd,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Q97.5 * sppb_external_sd,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Q97.5 * sppb_external_sd
  )) %>%
  mutate_if(is.numeric, round, 2)




# plot
ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = smd_data.final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_interval(aes(col = type)) +
  geom_point(data = numerical.data.smd.final, aes(Estimate, group = type), size = 3) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Standardised Mean Differences",
       title = "SMD estimates") +
  scale_x_continuous(limits = c(-0.5, 1.25),
                     breaks = seq(-1, 2, .25)) +
  theme_bw() +
  theme(legend.position = "none")

# density SMD plots
p1 <- ggplot(aes(x = intercept, y = factor(type)), data = smd_data.final %>%
         mutate(type = factor(type, levels = c(# "Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Relative effect estimates (SMD)") +
  scale_x_continuous(limits = c(-0.5, 1.25),
                     breaks = seq(-1, 2, .25)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

# tau estimates
p2 <- ggplot(aes(x = tau, y = factor(type)), data = smd_data.final %>%
         mutate(type = factor(type, levels = c(# "Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  labs(y = "",
       x = expression(paste(tau, " estimates (SMD)"))) +
  scale_x_continuous(limits = c(0, 1.5),
                     breaks = seq(-1, 2, .25)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

# plot grid
tiff("smd_plot.tiff", height = 7, width = 11, units = "in", res = 300)
plot_grid(p1, p2, labels = c('A', 'B'), label_size = 12)
dev.off()

# density MD plots
p1 <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Relative effect estimates (MD)") +
  scale_x_continuous(limits = c(-2, 4),
                     breaks = seq(-2, 4, 1)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

p2 <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  labs(y = "",
       x = expression(paste(tau, " estimates (MD)"))) +
  scale_x_continuous(limits = c(0, 4),
                     breaks = seq(-2, 4, 1)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()


p3 <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Relative effect estimates (MD)") +
  scale_x_continuous(limits = c(-2, 4),
                     breaks = seq(-2, 4, 1)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

p4 <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  labs(y = "",
       x = expression(paste(tau, " estimates (MD)"))) +
  scale_x_continuous(limits = c(0, 4),
                     breaks = seq(-2, 4, 1)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()


p5 <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Relative effect estimates (MD)") +
  scale_x_continuous(limits = c(-2, 4),
                     breaks = seq(-2, 4, 1)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

p6 <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  labs(y = "",
       x = expression(paste(tau, " estimates (MD)"))) +
  scale_x_continuous(limits = c(0, 4),
                     breaks = seq(-2, 4, 1)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

# creating complex plots
plot_1 <- (p1 / p2) + plot_annotation(title = "Method 1")
plot_2 <- (p3 / p4) + plot_annotation(title = "Method 2")
plot_3 <- (p5 / p6) + plot_annotation(title = "Method 3")

# combining them
ggpubr::ggarrange(plot_1, plot_2, plot_3, ncol = 3)
```



### SMD estimates and back transformation using the weighted internal SD

Cochrane recommendations stated that for a back transformation process using a scale included in the meta-analysis, it is required to multiply the SMD estimates by the internal SD reference of that specific scale.

```{r}
# unified dataset with all data rescaled using each the corresponding reference SD values
md_data_final <- draws %>%
  rbind(draws_ext %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_int %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_pre %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_post %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) # %>%
  # rbind(draws.w %>% 
  # mutate(intercept = intercept * sppb_internal_sd,
         # tau = tau * sppb_internal_sd)) 


# numerical data
numerical.data.smd.final <- fixef(model) %>%
  rbind(fixef(model_ext)) %>%
  rbind(fixef(model_int)) %>%
  rbind(fixef(model_pre)) %>%
  rbind(fixef(model_post)) %>%
  rbind(fixef(model_w)) %>%
  as_tibble() %>%
  mutate(type = factor(c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Pre pooled study-specific SD",
                         "Post pooled study-specific SD",
                                               "Weighted internal SD"))) %>%
  mutate(Estimate = ifelse(type == "Pooled MD", NA, Estimate)) %>%
  mutate(Q2.5 = ifelse(type == "Pooled MD", NA, Q2.5)) %>%
  mutate(Q97.5 = ifelse(type == "Pooled MD", NA, Q97.5)) %>%
  mutate_if(is.numeric, round, 2)


# numerical MD data
numerical.data.final <- fixef(model) %>%
  rbind(fixef(model_ext)) %>%
  rbind(fixef(model_int)) %>%
  rbind(fixef(model_pre)) %>%
  rbind(fixef(model_post)) %>%
  # rbind(fixef(model_w)) %>%
  as_tibble() %>%
  mutate(type = factor(c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                         "Study-specific pooled SD\n(at post-intervention)"))) %>%
  mutate(Estimate = case_when(
    type == "Pooled MD" ~ Estimate,
    type == "External SD" ~ Estimate * sppb_weighted_ref,
    type == "Internal SD" ~ Estimate * sppb_weighted_ref,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Estimate * sppb_weighted_ref,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Estimate * sppb_weighted_ref
  )) %>%
  mutate(Q2.5 = case_when(
    type == "Pooled MD" ~ Q2.5,
    type == "External SD" ~ Q2.5 * sppb_weighted_ref,
    type == "Internal SD" ~ Q2.5 * sppb_weighted_ref,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Q2.5 * sppb_weighted_ref,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Q2.5 * sppb_weighted_ref
  )) %>%
  mutate(Q97.5 = case_when(
    type == "Pooled MD" ~ Q97.5,
    type == "External SD" ~ Q97.5 * sppb_weighted_ref,
    type == "Internal SD" ~ Q97.5 * sppb_weighted_ref,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Q97.5 * sppb_weighted_ref,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Q97.5 * sppb_weighted_ref
  )) %>%
  mutate_if(is.numeric, round, 2)


# density SMD plots
ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = smd_data.final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD",
                                               "External SD",
                                               "Internal SD",
                                               "Pre pooled study-specific SD",
                                               "Post pooled study-specific SD")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Standardised Mean Differences",
       title = "SMD estimates") +
  scale_x_continuous(limits = c(-0.5, 1.25),
                     breaks = seq(-1, 2, .25)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()


# density MD plots
ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Relative effect estimates (MD)") +
  scale_x_continuous(limits = c(-2, 4),
                     breaks = seq(-2, 4, 1)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()
```




### SMD estimates and back transformation using the external SD

Cochrane recommendations stated that for a back transformation process using a scale that was not included in the meta-analysis, it is required to multiply the SMD estimates by a representative external SD reference of that specific scale.

```{r}
# unified dataset with all data rescaled using each the corresponding reference SD values
md_data_final <- draws %>%
  rbind(draws_ext %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_int %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_pre %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_post %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) # %>%
  # rbind(draws.w %>% 
  #  mutate(intercept = intercept * sppb_external_sd,
         # tau = tau * sppb_external_sd)) 


# numerical data
numerical.data.smd.final <- fixef(model) %>%
  rbind(fixef(model_ext)) %>%
  rbind(fixef(model_int)) %>%
  rbind(fixef(model_pre)) %>%
  rbind(fixef(model_post)) %>%
  rbind(fixef(model_w)) %>%
  as_tibble() %>%
  mutate(type = factor(c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Pre pooled study-specific SD",
                         "Post pooled study-specific SD",
                                               "Weighted internal SD"))) %>%
  mutate(Estimate = ifelse(type == "Pooled MD", NA, Estimate)) %>%
  mutate(Q2.5 = ifelse(type == "Pooled MD", NA, Q2.5)) %>%
  mutate(Q97.5 = ifelse(type == "Pooled MD", NA, Q97.5)) %>%
  mutate_if(is.numeric, round, 2)


# numerical MD data
numerical.data.final <- fixef(model) %>%
  rbind(fixef(model_ext)) %>%
  rbind(fixef(model_int)) %>%
  rbind(fixef(model_pre)) %>%
  rbind(fixef(model_post)) %>%
  # rbind(fixef(model_w)) %>%
  as_tibble() %>%
  mutate(type = factor(c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                         "Study-specific pooled SD\n(at post-intervention)"))) %>%
  mutate(Estimate = case_when(
    type == "Pooled MD" ~ Estimate,
    type == "External SD" ~ Estimate * sppb_external_sd,
    type == "Internal SD" ~ Estimate * sppb_external_sd,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Estimate * sppb_external_sd,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Estimate * sppb_external_sd
  )) %>%
  mutate(Q2.5 = case_when(
    type == "Pooled MD" ~ Q2.5,
    type == "External SD" ~ Q2.5 * sppb_external_sd,
    type == "Internal SD" ~ Q2.5 * sppb_external_sd,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Q2.5 * sppb_external_sd,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Q2.5 * sppb_external_sd
  )) %>%
  mutate(Q97.5 = case_when(
    type == "Pooled MD" ~ Q97.5,
    type == "External SD" ~ Q97.5 * sppb_external_sd,
    type == "Internal SD" ~ Q97.5 * sppb_external_sd,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Q97.5 * sppb_external_sd,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Q97.5 * sppb_external_sd
  )) %>%
  mutate_if(is.numeric, round, 2)


# density SMD plots
ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = smd_data.final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD",
                                               "External SD",
                                               "Internal SD",
                                               "Pre pooled study-specific SD",
                                               "Post pooled study-specific SD")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Standardised Mean Differences",
       title = "SMD estimates") +
  scale_x_continuous(limits = c(-0.5, 1.25),
                     breaks = seq(-1, 2, .25)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()


# density MD plots
ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD",
                                               "External SD",
                                               "Internal SD",
                                               "Pre pooled study-specific SD",
                                               "Post pooled study-specific SD")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Standardised Mean Differences",
       title = "MD estimates") +
  scale_x_continuous(limits = c(-2, 4),
                     breaks = seq(-2, 4, 1)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()
```



We then unify all these posterior draws in one database to continue with the posterior visualization of the parameters of interest. 

```{r, fig.height=8, fig.width=8}
# unified dataset with all posterior iterations of the meta-analysis models
smd_data.final <- draws %>%
  mutate(intercept = 0, 
         tau = 0) %>%
  rbind(draws_ext) %>%
  rbind(draws_int) %>%
  rbind(draws_def) %>%
  rbind(draws.w) %>%
  rbind(draws.inf %>%
          mutate(intercept = 0,
                 tau = 0)) %>%
  rbind(draws_ext.inf) %>%
  rbind(draws_int.inf) %>%
  rbind(draws_def.inf) %>%
  rbind(draws_w.inf) %>%
  rbind(draws.r %>%
          mutate(intercept = 0,
                 tau = 0)) %>%
  rbind(draws_ext.r) %>%
  rbind(draws_int.r) %>%
  rbind(draws_def.r) %>%
  rbind(draws_w.r) %>%
  rbind(draws_ext.n) %>%
  rbind(draws_int.n) %>%
  rbind(draws_def.n) %>%
  rbind(draws_w.n)
  

# unified dataset with all data rescaled using each the corresponding reference SD values
md_data_final <- draws %>%
  rbind(draws_ext %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_int %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_def %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws.w %>% 
  mutate(intercept = intercept * sppb_weighted_ref,
         tau = tau * sppb_weighted_ref)) %>%
  rbind(draws.inf) %>%
  rbind(draws_ext.inf %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_int.inf %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_def.inf %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_w.inf %>% 
  mutate(intercept = intercept * sppb_weighted_ref,
         tau = tau * sppb_weighted_ref)) %>%
  rbind(draws.r) %>%
  rbind(draws_ext.r %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_int.r %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_def.r %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_w.r %>% 
  mutate(intercept = intercept * sppb_weighted_ref,
         tau = tau * sppb_weighted_ref)) %>%
  rbind(draws_ext.n %>% 
  mutate(intercept = intercept * sppb_external_sd,
         tau = tau * sppb_external_sd)) %>%
  rbind(draws_int.n %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_def.n %>% 
  mutate(intercept = intercept * sppb_internal_sd,
         tau = tau * sppb_internal_sd)) %>%
  rbind(draws_w.n %>% 
  mutate(intercept = intercept * sppb_weighted_ref,
         tau = tau * sppb_weighted_ref))


### Pooled effect estimates

# numerical SMD data
numerical.data.smd.final <- fixef(model) %>%
  rbind(fixef(model_ext)) %>%
  rbind(fixef(model_int)) %>%
  rbind(fixef(model_default)) %>%
  rbind(fixef(model_w)) %>%
  rbind(fixef(model.inf)) %>%
  rbind(fixef(model_ext.inf)) %>%
  rbind(fixef(model_int.inf)) %>%
  rbind(fixef(model_default.inf)) %>%
  rbind(fixef(model_w.inf)) %>%
  rbind(fixef(model.r)) %>%
  rbind(fixef(model_ext.r)) %>%
  rbind(fixef(model_int.r)) %>%
  rbind(fixef(model_default.r)) %>%
  rbind(fixef(model_w.r)) %>%
  rbind(fixef(model_ext.n)) %>%
  rbind(fixef(model_int.n)) %>%
  rbind(fixef(model_default.n)) %>%
  rbind(fixef(model_w.n)) %>%
  as_tibble() %>%
  mutate(type = c(rep(c("Pooled MD",
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 3),
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"),
         model = c(rep("Vague priors", 5),
                   "Priors 5",
                   rep("Priors 2", 4),
                   "Priors 6",
                   rep("Priors 3", 4),
                   rep("Priors 4", 4))) %>%
  mutate(Estimate = ifelse(type == "Pooled MD", NA, Estimate)) %>%
  mutate(Q2.5 = ifelse(type == "Pooled MD", NA, Q2.5)) %>%
  mutate(Q97.5 = ifelse(type == "Pooled MD", NA, Q97.5)) %>%
  mutate_if(is.numeric, round, 2)

# numerical MD data 
numerical.data.final <- fixef(model) %>%
  rbind(fixef(model_ext)) %>%
  rbind(fixef(model_int)) %>%
  rbind(fixef(model_default)) %>%
  rbind(fixef(model_w)) %>%
  rbind(fixef(model.inf)) %>%
  rbind(fixef(model_ext.inf)) %>%
  rbind(fixef(model_int.inf)) %>%
  rbind(fixef(model_default.inf)) %>%
  rbind(fixef(model_w.inf)) %>%
  rbind(fixef(model.r)) %>%
  rbind(fixef(model_ext.r)) %>%
  rbind(fixef(model_int.r)) %>%
  rbind(fixef(model_default.r)) %>%
  rbind(fixef(model_w.r)) %>%
  rbind(fixef(model_ext.n)) %>%
  rbind(fixef(model_int.n)) %>%
  rbind(fixef(model_default.n)) %>%
  rbind(fixef(model_w.n)) %>%
  as_tibble() %>%
  mutate(type = c(rep(c("Pooled MD",
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 3),
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"),
         model = c(rep("Vague priors", 5),
                   "Priors 5",
                   rep("Priors 2", 4),
                   "Priors 6",
                   rep("Priors 3", 4),
                   rep("Priors 4", 4))) %>%
  mutate(Estimate = case_when(
    type == "Pooled MD" ~ Estimate,
    type == "External SD reference model" ~ Estimate * sppb_external_sd,
    type == "Internal SD reference model" ~ Estimate * sppb_internal_sd,
    type == "Within-study\npooled sample SD model" ~ Estimate * sppb_internal_sd,
    type == "Weighted internal SD reference" ~ Estimate * sppb_weighted_ref
  )) %>%
  mutate(Q2.5 = case_when(
    type == "Pooled MD" ~ Q2.5,
    type == "External SD reference model" ~ Q2.5 * sppb_external_sd,
    type == "Internal SD reference model" ~ Q2.5 * sppb_internal_sd,
    type == "Within-study\npooled sample SD model" ~ Q2.5 * sppb_internal_sd,
    type == "Weighted internal SD reference" ~ Q2.5 * sppb_weighted_ref
  )) %>%
  mutate(Q97.5 = case_when(
    type == "Pooled MD" ~ Q97.5,
    type == "External SD reference model" ~ Q97.5 * sppb_external_sd,
    type == "Internal SD reference model" ~ Q97.5 * sppb_internal_sd,
    type == "Within-study\npooled sample SD model" ~ Q97.5 * sppb_internal_sd,
    type == "Weighted internal SD reference" ~ Q97.5 * sppb_weighted_ref
  )) %>%
  mutate_if(is.numeric, round, 2)


# SMDs estimates visualization

nice_plot.1 <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = smd_data.final %>%
         mutate(model = factor(model, levels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors")),
                type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")))) +
  stat_interval(aes(group = model, col = model), position = position_dodge(0.75)) +
  geom_point(data = numerical.data.smd.final %>%
               mutate(type = factor(type, levels = c("Pooled MD",
                                                     "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")),
                      model = factor(model, levels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"),
                               labels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"))), aes(Estimate, group = model), size = 3,
             position = position_dodge(0.75)) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Standardised Mean Differences",
       title = "SMD estimates") +
  scale_x_continuous(limits = c(-0.5, 1.25),
                     breaks = seq(-1, 2, .25)) +
  scale_color_nejm(breaks = c("Vague priors",
                                                 "Priors 2",
                                                 "Priors 3",
                                                 "Priors 4",
                                                 "Priors 5",
                                                 "Priors 6")) +
  labs(col = "Prior distributions") +
  theme_bw()

# MD estimates visualization
# plot 1 for MD values
nice_plot.2 <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(model = factor(model, levels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors")),
                type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")))) +
  stat_interval(aes(group = model, col = model), position = position_dodge(0.75)) +
  geom_point(data = numerical.data.final %>%
               mutate(type = factor(type, levels = c("Pooled MD",
                                                     "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")),
                      model = factor(model, levels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"),
                               labels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"))), aes(Estimate, group = model), size = 3,
             position = position_dodge(0.75)) +
  geom_vline(xintercept = 0, size = .5, linetype = 2) +
  labs(y = "",
       x = "Mean Differences",
       title = "MD estimates") +
  scale_x_continuous(limits = c(-0.75, 2.5),
                     breaks = seq(-1, 2.5, .5)) +
  scale_color_nejm(breaks = c("Vague priors",
                                                 "Priors 2",
                                                 "Priors 3",
                                                 "Priors 4",
                                                 "Priors 5",
                                                 "Priors 6")) +
  labs(col = "Prior distributions") +
  theme_bw()

# combining effect estimates plots
effect_plot <- nice_plot.1 + nice_plot.2


  
### Between-study SD estimates

# numerical data as SMDs
het.numerical.data <- brms::posterior_summary(model)[2, ] %>%
  rbind(posterior_summary(model_ext)[2, ]) %>%
  rbind(posterior_summary(model_int)[2, ]) %>%
  rbind(posterior_summary(model_default)[2, ]) %>%
  rbind(posterior_summary(model_w)[2, ]) %>%
  rbind(posterior_summary(model.inf)[2, ]) %>%
  rbind(posterior_summary(model_ext.inf)[2, ]) %>%
  rbind(posterior_summary(model_int.inf)[2, ]) %>%
  rbind(posterior_summary(model_w.inf)[2, ]) %>% 
  rbind(posterior_summary(model_default.inf)[2, ]) %>%
  rbind(posterior_summary(model.r)[2, ]) %>%
  rbind(posterior_summary(model_ext.r)[2, ]) %>%
  rbind(posterior_summary(model_int.r)[2, ]) %>%
  rbind(posterior_summary(model_default.r)[2, ]) %>%
  rbind(posterior_summary(model_w.r)[2, ]) %>%
  rbind(posterior_summary(model_ext.n)[2, ]) %>%
  rbind(posterior_summary(model_int.n)[2, ]) %>%
  rbind(posterior_summary(model_default.n)[2, ]) %>%
  rbind(posterior_summary(model_w.n)[2, ]) %>%
  as_tibble() %>%
  mutate(type = c(rep(c("Pooled MD",
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 3),
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"),
         model = c(rep("Vague priors", 5),
                   "Priors 5",
                   rep("Priors 2", 4),
                   "Priors 6",
                   rep("Priors 3", 4),
                   rep("Priors 4", 4))) %>%
  mutate(Estimate = ifelse(type == "Pooled MD", NA, Estimate)) %>%
  mutate(Q2.5 = ifelse(type == "Pooled MD", NA, Q2.5)) %>%
  mutate(Q97.5 = ifelse(type == "Pooled MD", NA, Q97.5)) %>%
  mutate_if(is.numeric, round, 2)

# rescaled between-study SD 
het.numerical.data.rescaled <- brms::posterior_summary(model)[2, ] %>%
  rbind(posterior_summary(model_ext)[2, ]) %>%
  rbind(posterior_summary(model_int)[2, ]) %>%
  rbind(posterior_summary(model_default)[2, ]) %>%
  rbind(posterior_summary(model_w)[2, ]) %>%
  rbind(posterior_summary(model.inf)[2, ]) %>%
  rbind(posterior_summary(model_ext.inf)[2, ]) %>%
  rbind(posterior_summary(model_int.inf)[2, ]) %>%
  rbind(posterior_summary(model_w.inf)[2, ]) %>% 
  rbind(posterior_summary(model_default.inf)[2, ]) %>%
  rbind(posterior_summary(model.r)[2, ]) %>%
  rbind(posterior_summary(model_ext.r)[2, ]) %>%
  rbind(posterior_summary(model_int.r)[2, ]) %>%
  rbind(posterior_summary(model_default.r)[2, ]) %>%
  rbind(posterior_summary(model_w.r)[2, ]) %>%
  rbind(posterior_summary(model_ext.n)[2, ]) %>%
  rbind(posterior_summary(model_int.n)[2, ]) %>%
  rbind(posterior_summary(model_default.n)[2, ]) %>%
  rbind(posterior_summary(model_w.n)[2, ]) %>%
  as_tibble() %>%
  mutate(type = c(rep(c("Pooled MD",
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 3),
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"),
         model = c(rep("Vague priors", 5),
                   "Priors 5",
                   rep("Priors 2", 4),
                   "Priors 6",
                   rep("Priors 3", 4),
                   rep("Priors 4", 4))) %>%
  mutate(Estimate = case_when(
    type == "Pooled MD" ~ Estimate,
    type == "External SD reference model" ~ Estimate * sppb_external_sd,
    type == "Internal SD reference model" ~ Estimate * sppb_internal_sd,
    type == "Within-study\npooled sample SD model" ~ Estimate * sppb_internal_sd,
    type == "Weighted internal SD reference" ~ Estimate * sppb_weighted_ref 
  )) %>%
  mutate(Q2.5 = case_when(
    type == "Pooled MD" ~ Q2.5,
    type == "External SD reference model" ~ Q2.5 * sppb_external_sd,
    type == "Internal SD reference model" ~ Q2.5 * sppb_internal_sd,
    type == "Within-study\npooled sample SD model" ~ Q2.5 * sppb_internal_sd,
    type == "Weighted internal SD reference" ~ Q2.5 * sppb_weighted_ref
  )) %>%
  mutate(Q97.5 = case_when(
    type == "Pooled MD" ~ Q97.5,
    type == "External SD reference model" ~ Q97.5 * sppb_external_sd,
    type == "Internal SD reference model" ~ Q97.5 * sppb_internal_sd,
    type == "Within-study\npooled sample SD model" ~ Q97.5 * sppb_internal_sd,
    type == "Weighted internal SD reference" ~ Q97.5 * sppb_weighted_ref
  )) %>%
  mutate_if(is.numeric, round, 2)


# plot for heterogeneity in SMD terms
nice_plot.3 <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = smd_data.final %>%
         mutate(model = factor(model, levels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors")),
                type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")))) +
  stat_interval(aes(group = model, col = model), position = position_dodge(0.75)) +
  geom_point(data = het.numerical.data %>%
               mutate(type = factor(type, levels = c("Pooled MD",
                                                     "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")),
                      model = factor(model, levels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"),
                               labels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"))), aes(Estimate, group = model), size = 3,
             position = position_dodge(0.75)) +
  labs(y = "",
       x = expression(paste(tau)),
       title = "Between-study SD") +
  scale_x_continuous(limits = c(0, 1.5),
                     breaks = seq(-1, 2.5, .25)) +
  scale_color_nejm(breaks = c("Vague priors",
                                                 "Priors 2",
                                                 "Priors 3",
                                                 "Priors 4",
                                                 "Priors 5",
                                                 "Priors 6")) +
  labs(col = "Prior distributions") +
  theme_bw()


# back-conversion visualization
nice_plot.4 <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final %>%
         mutate(model = factor(model, levels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors")),
                type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")))) +
  stat_interval(aes(group = model, col = model), position = position_dodge(0.75)) +
  geom_point(data = het.numerical.data.rescaled %>%
               mutate(type = factor(type, levels = c("Pooled MD",
                                                     "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")),
                      model = factor(model, levels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"),
                               labels = c("Priors 6",
                                                 "Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"))), aes(Estimate, group = model), size = 3,
             position = position_dodge(0.75)) +
  labs(y = "",
       x = expression(paste(tau)),
       title = "Between-study SD (MD estimates)") +
  scale_x_continuous(limits = c(0, 3.25),
                     breaks = seq(-1, 5.5, .5)) +
  scale_color_nejm(breaks = c("Vague priors",
                                                 "Priors 2",
                                                 "Priors 3",
                                                 "Priors 4",
                                                 "Priors 5",
                                                 "Priors 6")) +
  labs(col = "Prior distributions") +
  theme_bw()

# combining plots
het.plot <- nice_plot.3 + nice_plot.4


# plot!
ggarrange(nice_plot.1, nice_plot.2, nice_plot.3, nice_plot.4, ncol = 2, nrow = 2, common.legend = TRUE, legend = "bottom")
```



## Barthel index

Let's save the SD references for this outcome.

```{r}
# external SD reference used for standardization
external_sd.bi <- 25.39

# internal SD reference used for standardization
internal_sd.bi <- sum(bi_data$pre_sd_pooled) / nrow(bi_data)

# internal SD reference used for standardization
internal_sd.bi.post <- sum(bi_data$post_sd_pooled) / nrow(bi_data)

## weighted internal SD reference
weighted_sd.bi <- 17.209999
```


#### Bit of data wrangling

```{r}
bi_data <- bi_data %>%
               mutate(studyID = case_when(
                 studyID == "Martinez-Velilla, 2019" ~ "Martinez-Velilla1",
                 studyID == "Martinez-Velilla, 2021" ~ "Martinez-Velilla2",
                 studyID == "Martinez-Velilla, 2022" ~ "Martinez-Velilla3",
                 studyID == "de Morton, 2007" ~ "de Morton, 2007",
                 studyID == "Casas-Herrero, 2022" ~ "Casas-Herrero, 2022"
               ),
               diff_w = diff / weighted_sd.bi,
         se_diff_w = se_diff / weighted_sd.bi)
```



## Fitting our meta-analysis models

```{r, results='hide', message=FALSE, warning=FALSE, error=FALSE}
# for reproducibility sake
set.seed(28032023)

# multilevel random-intercept meta-analysis using MD 
model.bi <- brm(diff | se(se_diff, sigma = TRUE) ~ 1 + (1 | studyID),
             data = bi_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-analysis using SMDs rescaled using an external SD reference 
model_ext.bi <- brm(diff_ext | se(se_diff_ext, sigma = TRUE) ~ 1 + (1 | studyID),
             data = bi_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-analysis using SMDs rescaled using an internal SD reference 
model_int.bi <- brm(diff_int | se(se_diff_int, sigma = TRUE) ~ 1 + (1 | studyID),
             data = bi_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-analysis using SMDs rescaled using the pooled SD of each study
model_pre.bi <- brm(diff_pre | se(se_diff_pre, sigma = TRUE) ~ 1 + (1 | studyID),
             data = bi_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-analysis using SMDs rescaled using the pooled SD of each study
model_post.bi <- brm(diff_post | se(se_diff_post, sigma = TRUE) ~ 1 + (1 | studyID),
             data = bi_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)

# multilevel random-intercept meta-analysis using SMDs rescaled using a weighted internal SD reference
model.w.bi <- brm(diff_w | se(se_diff_w) ~ 1 + (1 | studyID),
             data = bi_data,
             family = gaussian(),
             prior = vague_priors,
             control = list(adapt_delta = 0.99),
             iter = 4000, warmup = 1000)
```
  

#### Convergence analysis

First, let's check if our model reached the convergence. We first check the mixing of the Markov Chain Monte-Carlo simulations, and we then observe the Potential Scale Reduction Factor ($\hat{R}$ parameter) which should be smaller than 1.05.

```{r}
# good mixing of our predictive chains
plot(model.bi)

# posterior predictive check
pp_plot <- pp_check(model.bi, ndraws = 50)
pp_plot.1 <- pp_check(model_pre.bi, ndraws = 50)
pp_plot.2 <- pp_check(model_post.bi, ndraws = 50)
pp_plot.3 <- pp_check(model_int.bi, ndraws = 50)
pp_plot.4 <- pp_check(model_ext.bi, ndraws = 50)

# observed Rhat value below 1.05
summary(model.bi)
```


### Extracting and visualizing posterior tidy draws

First, we extract the posterior draws for each model corresponding to the random intercept for each study and the between-study heterogeneity. Additionally, we create a variable (`type`) that indicates the meta-analysis model.

```{r}
# extract the posterior draws of the models
## observed mean differences
draws.bi <- posterior_samples(model.bi, c("^b", "^sd")) %>%
  mutate(type = "Pooled MD")

## mean differences rescaled using an external SD reference
draws_ext.bi <- posterior_samples(model_ext.bi, c("^b", "^sd")) %>%
  mutate(type = "External SD")

## mean differences rescaled using an internal SD reference
draws_int.bi <- posterior_samples(model_int.bi, c("^b", "^sd")) %>%
  mutate(type = "Internal SD")

## mean differences rescaled using the pooled SD of each study
draws_pre.bi <- posterior_samples(model_pre.bi, c("^b", "^sd")) %>%
  mutate(type = "Study-specific pooled SD\n(at pre-intervention)")

## mean differences rescaled using the pooled SD of each study
draws_post.bi <- posterior_samples(model_post.bi, c("^b", "^sd")) %>%
  mutate(type = "Study-specific pooled SD\n(at post-intervention)")


# change the variables' names for simplicity sake
names(draws.bi) <- c("intercept", "tau", "type")

names(draws_ext.bi) <- c("intercept", "tau", "type")

names(draws_int.bi) <- c("intercept", "tau", "type")

names(draws_pre.bi) <- c("intercept", "tau", "type")

names(draws_post.bi) <- c("intercept", "tau", "type")


# unified dataset with all posterior iterations of the meta-analysis models
smd_data.final.bi <- # draws %>%
  # mutate(intercept = 0, 
         # tau = 0) %>%
  rbind(draws_ext.bi) %>%
  rbind(draws_int.bi) %>%
  rbind(draws_pre.bi) %>%
  rbind(draws_post.bi)
  

# unified dataset with all data rescaled using each the corresponding reference SD values
md_data_final.bi <- draws.bi %>%
  rbind(draws_ext.bi %>% 
  mutate(intercept = intercept * weighted_sd.bi,
         tau = tau * weighted_sd.bi)) %>%
  rbind(draws_int.bi %>% 
  mutate(intercept = intercept * weighted_sd.bi,
         tau = tau * weighted_sd.bi)) %>%
  rbind(draws_pre.bi %>% 
  mutate(intercept = intercept * weighted_sd.bi,
         tau = tau * weighted_sd.bi)) %>%
  rbind(draws_post.bi %>% 
  mutate(intercept = intercept * weighted_sd.bi,
         tau = tau * weighted_sd.bi)) 
```

```{r}
# numerical data
numerical.data.smd.final.bi <- # fixef(model) %>%
  rbind(fixef(model_ext.bi)) %>%
  rbind(fixef(model_int.bi)) %>%
  rbind(fixef(model_pre.bi)) %>%
  rbind(fixef(model_post.bi)) %>%
  as_tibble() %>%
  mutate(type = factor(c("External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                         "Study-specific pooled SD\n(at post-intervention)"))) %>%
  # mutate(Estimate = ifelse(type == "Pooled MD", NA, Estimate)) %>%
  # mutate(Q2.5 = ifelse(type == "Pooled MD", NA, Q2.5)) %>%
  # mutate(Q97.5 = ifelse(type == "Pooled MD", NA, Q97.5)) %>%
  mutate_if(is.numeric, round, 2)

# tau estimates
posterior_summary(model_int.bi)[2, ] * internal_sd.bi

# numerical MD data
numerical.data.final.bi <- fixef(model.bi) %>%
  rbind(fixef(model_ext.bi)) %>%
  rbind(fixef(model_int.bi)) %>%
  rbind(fixef(model_pre.bi)) %>%
  rbind(fixef(model_post.bi)) %>%
  as_tibble() %>%
  mutate(type = factor(c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                         "Study-specific pooled SD\n(at post-intervention)"))) %>%
  mutate(Estimate = case_when(
    type == "Pooled MD" ~ Estimate,
    type == "External SD" ~ Estimate * external_sd.bi,
    type == "Internal SD" ~ Estimate * internal_sd.bi,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Estimate * internal_sd.bi,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Estimate * internal_sd.bi.post
  )) %>%
  mutate(Q2.5 = case_when(
    type == "Pooled MD" ~ Q2.5,
    type == "External SD" ~ Q2.5 * external_sd.bi,
    type == "Internal SD" ~ Q2.5 * internal_sd.bi,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Q2.5 * internal_sd.bi,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Q2.5 * internal_sd.bi.post
  )) %>%
  mutate(Q97.5 = case_when(
    type == "Pooled MD" ~ Q97.5,
    type == "External SD" ~ Q97.5 * external_sd.bi,
    type == "Internal SD" ~ Q97.5 * internal_sd.bi,
    type == "Study-specific pooled SD\n(at pre-intervention)" ~ Q97.5 * internal_sd.bi,
    type == "Study-specific pooled SD\n(at post-intervention)" ~ Q97.5 * internal_sd.bi.post
  )) %>%
  mutate_if(is.numeric, round, 2)




# plot
# density SMD plots
p1.bi <- ggplot(aes(x = intercept, y = factor(type)), data = smd_data.final.bi %>%
         mutate(type = factor(type, levels = c(# "Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Relative effect estimates (SMD)") +
  scale_x_continuous(limits = c(-0.75, 1),
                     breaks = seq(-1, 2, .25)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

# tau estimates
p2.bi <- ggplot(aes(x = tau, y = factor(type)), data = smd_data.final.bi %>%
         mutate(type = factor(type, levels = c(# "Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  labs(y = "",
       x = expression(paste(tau, " estimates (SMD)"))) +
  scale_x_continuous(limits = c(0, 1.5),
                     breaks = seq(-1, 2, .25)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

# plot grid
plot_grid(p1.bi, p2.bi, labels = c('A', 'B'), label_size = 12)


# density MD plots
p1.bi <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final.bi %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Relative effect estimates (MD)") +
  scale_x_continuous(limits = c(-8, 18),
                     breaks = seq(-10, 20, 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

p2.bi <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final.bi %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  labs(y = "",
       x = expression(paste(tau, " estimates (MD)"))) +
  scale_x_continuous(limits = c(0, 20),
                     breaks = seq(-2, 20, 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()


p3.bi <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final.bi %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Relative effect estimates (MD)") +
  scale_x_continuous(limits = c(-8, 18),
                     breaks = seq(-10, 20, 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

p4.bi <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final.bi %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  labs(y = "",
       x = expression(paste(tau, " estimates (MD)"))) +
  scale_x_continuous(limits = c(0, 20),
                     breaks = seq(-2, 20, 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()


p5.bi <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final.bi %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  geom_vline(xintercept = 0, col = "black", size = 0.5, linetype = 2) +
  labs(y = "",
       x = "Relative effect estimates (MD)") +
  scale_x_continuous(limits = c(-8, 18),
                     breaks = seq(-10, 20, 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

p6.bi <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final.bi %>%
         mutate(type = factor(type, levels = c("Pooled MD",
                                               "External SD",
                                               "Internal SD",
                                               "Study-specific pooled SD\n(at pre-intervention)",
                                               "Study-specific pooled SD\n(at post-intervention)")))) +
  stat_halfeye(aes(fill = type), slab_alpha = 0.5) +
  labs(y = "",
       x = expression(paste(tau, " estimates (MD)"))) +
  scale_x_continuous(limits = c(0, 20),
                     breaks = seq(-2, 20, 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  scale_fill_lancet()

# building complex plots
plot_1.bi <- (p1.bi / p2.bi) + plot_annotation(title = "Method 1")
plot_2.bi <- (p3.bi / p4.bi) + plot_annotation(title = "Method 2")
plot_3.bi <- (p5.bi / p6.bi) + plot_annotation(title = "Method 3")

# combining them
ggpubr::ggarrange(plot_1.bi, plot_2.bi, plot_3.bi, ncol = 3)
```


We then unify all these posterior draws in one database to continue with the posterior visualization of the parameters of interest. 

```{r, fig.height=8, fig.width=8}
# unified dataset with all posterior iterations of the meta-analysis models
smd_data.final.bi <- draws.bi %>%
  mutate(intercept = 0, 
         tau = 0) %>%
  rbind(draws_ext.bi) %>%
  rbind(draws_int.bi) %>%
  rbind(draws_def.bi) %>%
  rbind(draws_w.bi) %>%
  rbind(draws.inf.bi %>%
          mutate(intercept = 0,
                 tau = 0)) %>%
  rbind(draws_ext.inf.bi) %>%
  rbind(draws_int.inf.bi) %>%
  rbind(draws_def.inf.bi) %>%
  rbind(draws_w.inf.bi) %>%
  rbind(draws_ext.r.bi) %>%
  rbind(draws_int.r.bi) %>%
  rbind(draws_def.r.bi) %>%
  rbind(draws_w.r.bi) %>%
  rbind(draws_ext.n.bi) %>%
  rbind(draws_int.n.bi) %>%
  rbind(draws_def.n.bi) %>%
  rbind(draws_w.n.bi)
  

# unified dataset with all data rescaled using each the corresponding reference SD values
md_data_final.bi <- draws.bi %>%
  rbind(draws_ext.bi %>% 
  mutate(intercept = intercept * external_sd.bi,
         tau = tau * external_sd.bi)) %>%
  rbind(draws_int.bi %>% 
  mutate(intercept = intercept * internal_sd.bi,
         tau = tau * internal_sd.bi)) %>%
  rbind(draws_def.bi %>% 
  mutate(intercept = intercept * internal_sd.bi,
         tau = tau * internal_sd.bi)) %>%
  rbind(draws_w.bi %>% 
  mutate(intercept = intercept * weighted_sd.bi,
         tau = tau * weighted_sd.bi)) %>%
  rbind(draws.inf.bi) %>%
  rbind(draws_ext.inf.bi %>% 
  mutate(intercept = intercept * external_sd.bi,
         tau = tau * external_sd.bi)) %>%
  rbind(draws_int.inf.bi %>% 
  mutate(intercept = intercept * internal_sd.bi,
         tau = tau * internal_sd.bi)) %>%
  rbind(draws_def.inf.bi %>% 
  mutate(intercept = intercept * internal_sd.bi,
         tau = tau * internal_sd.bi)) %>%
  rbind(draws_w.inf.bi %>% 
  mutate(intercept = intercept * weighted_sd.bi,
         tau = tau * weighted_sd.bi)) %>%
  rbind(draws_ext.r.bi %>% 
  mutate(intercept = intercept * external_sd.bi,
         tau = tau * external_sd.bi)) %>%
  rbind(draws_int.r.bi %>% 
  mutate(intercept = intercept * internal_sd.bi,
         tau = tau * internal_sd.bi)) %>%
  rbind(draws_def.r.bi %>% 
  mutate(intercept = intercept * internal_sd.bi,
         tau = tau * internal_sd.bi)) %>%
  rbind(draws_w.r.bi %>% 
  mutate(intercept = intercept * weighted_sd.bi,
         tau = tau * weighted_sd.bi)) %>%
  rbind(draws_ext.n.bi %>% 
  mutate(intercept = intercept * external_sd.bi,
         tau = tau * external_sd.bi)) %>%
  rbind(draws_int.n.bi %>% 
  mutate(intercept = intercept * internal_sd.bi,
         tau = tau * internal_sd.bi)) %>%
  rbind(draws_def.n.bi %>% 
  mutate(intercept = intercept * internal_sd.bi,
         tau = tau * internal_sd.bi)) %>%
  rbind(draws_w.n.bi %>% 
  mutate(intercept = intercept * weighted_sd.bi,
         tau = tau * weighted_sd.bi))


### Pooled effect estimates

# numerical SMD data
numerical.data.smd.final.bi <- fixef(model.bi) %>%
  rbind(fixef(model_ext.bi)) %>%
  rbind(fixef(model_int.bi)) %>%
  rbind(fixef(model_default.bi)) %>%
  rbind(fixef(model.w.bi)) %>%
  rbind(fixef(model.inf.bi)) %>%
  rbind(fixef(model_ext.inf.bi)) %>%
  rbind(fixef(model_int.inf.bi)) %>%
  rbind(fixef(model_default.inf.bi)) %>%
  rbind(fixef(model.w.inf.bi)) %>%
  rbind(fixef(model_ext.r.bi)) %>%
  rbind(fixef(model_int.r.bi)) %>%
  rbind(fixef(model_default.r.bi)) %>%
  rbind(fixef(model.w.r.bi)) %>%
  rbind(fixef(model_ext.n.bi)) %>%
  rbind(fixef(model_int.n.bi)) %>%
  rbind(fixef(model_default.n.bi)) %>%
  rbind(fixef(model.w.n.bi)) %>%
  as_tibble() %>%
  mutate(type = c(rep(c("Pooled MD",
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 2),
                  rep(c("External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 2)),
         model = c(rep("Vague priors", 5),
                   "Priors 5",
                   rep("Priors 2", 4),
                   rep("Priors 3", 4),
                   rep("Priors 4", 4))) %>%
  mutate(Estimate = ifelse(type == "Pooled MD", NA, Estimate)) %>%
  mutate(Q2.5 = ifelse(type == "Pooled MD", NA, Q2.5)) %>%
  mutate(Q97.5 = ifelse(type == "Pooled MD", NA, Q97.5)) %>%
  mutate_if(is.numeric, round, 2)

# numerical MD data 
numerical.data.final.bi <- fixef(model.bi) %>%
  rbind(fixef(model_ext.bi)) %>%
  rbind(fixef(model_int.bi)) %>%
  rbind(fixef(model_default.bi)) %>%
  rbind(fixef(model.w.bi)) %>%
  rbind(fixef(model.inf.bi)) %>%
  rbind(fixef(model_ext.inf.bi)) %>%
  rbind(fixef(model_int.inf.bi)) %>%
  rbind(fixef(model_default.inf.bi)) %>%
  rbind(fixef(model.w.inf.bi)) %>%
  rbind(fixef(model_ext.r.bi)) %>%
  rbind(fixef(model_int.r.bi)) %>%
  rbind(fixef(model_default.r.bi)) %>%
  rbind(fixef(model.w.r.bi)) %>%
  rbind(fixef(model_ext.n.bi)) %>%
  rbind(fixef(model_int.n.bi)) %>%
  rbind(fixef(model_default.n.bi)) %>%
  rbind(fixef(model.w.n.bi)) %>%
  as_tibble() %>%
  mutate(type = c(rep(c("Pooled MD",
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 2),
                  rep(c("External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 2)),
         model = c(rep("Vague priors", 5),
                   "Priors 5",
                   rep("Priors 2", 4),
                   rep("Priors 3", 4),
                   rep("Priors 4", 4))) %>%
  mutate(Estimate = case_when(
    type == "Pooled MD" ~ Estimate,
    type == "External SD reference model" ~ Estimate * external_sd.bi,
    type == "Internal SD reference model" ~ Estimate * internal_sd.bi,
    type == "Within-study\npooled sample SD model" ~ Estimate * internal_sd.bi,
    type == "Weighted internal SD reference" ~ Estimate * weighted_sd.bi
  )) %>%
  mutate(Q2.5 = case_when(
    type == "Pooled MD" ~ Q2.5,
    type == "External SD reference model" ~ Q2.5 * external_sd.bi,
    type == "Internal SD reference model" ~ Q2.5 * internal_sd.bi,
    type == "Within-study\npooled sample SD model" ~ Q2.5 * internal_sd.bi,
    type == "Weighted internal SD reference" ~ Q2.5 * weighted_sd.bi
  )) %>%
  mutate(Q97.5 = case_when(
    type == "Pooled MD" ~ Q97.5,
    type == "External SD reference model" ~ Q97.5 * external_sd.bi,
    type == "Internal SD reference model" ~ Q97.5 * internal_sd.bi,
    type == "Within-study\npooled sample SD model" ~ Q97.5 * internal_sd.bi,
    type == "Weighted internal SD reference" ~ Q97.5 * weighted_sd.bi
  )) %>%
  mutate_if(is.numeric, round, 2)


# SMDs estimates visualization
# plot 1
nice_plot.5 <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = smd_data.final.bi %>%
         mutate(model = factor(model, levels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors")),
                type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")))) +
  stat_interval(aes(group = model, col = model), position = position_dodge(0.75)) +
  geom_point(data = numerical.data.smd.final.bi %>%
               mutate(type = factor(type, levels = c("Pooled MD",
                                                     "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")),
                      model = factor(model, levels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"),
                               labels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"))), aes(Estimate, group = model), size = 3,
             position = position_dodge(0.75)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.5) +
  labs(y = "",
       x = "Standardised Mean Differences",
       title = "SMD estimates") +
  scale_x_continuous(limits = c(-0.5, 1.25),
                     breaks = seq(-1, 2, .25)) +
  scale_color_nejm(breaks = c("Vague priors",
                                                 "Priors 2",
                                                 "Priors 3",
                                                 "Priors 4",
                                                 "Priors 5")) +
  labs(col = "Prior distributions") +
  theme_bw()


# MD plot
# plot 1
nice_plot.6 <- ggplot(aes(x = intercept, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final.bi %>%
         mutate(model = factor(model, levels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors")),
                type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")))) +
  stat_interval(aes(group = model, col = model), position = position_dodge(0.75)) +
  geom_point(data = numerical.data.final.bi %>%
               mutate(type = factor(type, levels = c("Pooled MD",
                                                     "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")),
                      model = factor(model, levels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"),
                               labels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"))), aes(Estimate, group = model), size = 3,
             position = position_dodge(0.75)) +
  geom_vline(xintercept = 0, linetype = 2, size = 1/2) +
  labs(y = "",
       x = "Mean Differences",
       title = "MD estimates") +
  scale_x_continuous(breaks = seq(-5, 15, 1),
                     limits = c(-5, 15)) +
  scale_color_nejm(breaks = c("Vague priors",
                                                 "Priors 2",
                                                 "Priors 3",
                                                 "Priors 4",
                                                 "Priors 5")) +
  labs(col = "Prior distributions") +
  theme_bw()


# combining effect estimates plots
effect_plot.bi <- smd_plot.bi + md_plot.bi
effect_plot.bi <- (nice_plot.5 + theme(legend.position = "none")) + nice_plot.6

### Between-study SD estimates

# numerical data as SMDs
het.numerical.data.bi <- brms::posterior_summary(model.bi)[2, ] %>%
  rbind(posterior_summary(model_ext.bi)[2, ]) %>%
  rbind(posterior_summary(model_int.bi)[2, ]) %>%
  rbind(posterior_summary(model_default.bi)[2, ]) %>%
  rbind(posterior_summary(model.w.bi)[2, ]) %>%
  rbind(posterior_summary(model.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model_ext.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model_int.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model_default.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model.w.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model_ext.r.bi)[2, ]) %>%
  rbind(posterior_summary(model_int.r.bi)[2, ]) %>%
  rbind(posterior_summary(model_default.r.bi)[2, ]) %>%
  rbind(posterior_summary(model.w.r.bi)[2, ]) %>%
  rbind(posterior_summary(model_ext.n.bi)[2, ]) %>%
  rbind(posterior_summary(model_int.n.bi)[2, ]) %>%
  rbind(posterior_summary(model_default.n.bi)[2, ]) %>%
  rbind(posterior_summary(model.w.n.bi)[2, ]) %>%
  as_tibble() %>%
  mutate(type = c(rep(c("Pooled MD",
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 2),
                  rep(c("External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 2)),
         model = c(rep("Vague priors", 5),
                   "Priors 5",
                   rep("Priors 2", 4),
                   rep("Priors 3", 4),
                   rep("Priors 4", 4))) %>%
  mutate(Estimate = ifelse(type == "Pooled MD", NA, Estimate)) %>%
  mutate(Q2.5 = ifelse(type == "Pooled MD", NA, Q2.5)) %>%
  mutate(Q97.5 = ifelse(type == "Pooled MD", NA, Q97.5)) %>%
  mutate_if(is.numeric, round, 2)

# rescaled between-study SD 
het.numerical.data.rescaled.bi <- brms::posterior_summary(model.bi)[2, ] %>%
  rbind(posterior_summary(model_ext.bi)[2, ]) %>%
  rbind(posterior_summary(model_int.bi)[2, ]) %>%
  rbind(posterior_summary(model_default.bi)[2, ]) %>%
  rbind(posterior_summary(model.w.bi)[2, ]) %>%
  rbind(posterior_summary(model.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model_ext.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model_int.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model_default.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model.w.inf.bi)[2, ]) %>%
  rbind(posterior_summary(model_ext.r.bi)[2, ]) %>%
  rbind(posterior_summary(model_int.r.bi)[2, ]) %>%
  rbind(posterior_summary(model_default.r.bi)[2, ]) %>%
  rbind(posterior_summary(model.w.r.bi)[2, ]) %>%
  rbind(posterior_summary(model_ext.n.bi)[2, ]) %>%
  rbind(posterior_summary(model_int.n.bi)[2, ]) %>%
  rbind(posterior_summary(model_default.n.bi)[2, ]) %>%
  rbind(posterior_summary(model.w.n.bi)[2, ]) %>%
  as_tibble() %>%
  mutate(type = c(rep(c("Pooled MD",
                  "External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 2),
                  rep(c("External SD reference model",
                  "Internal SD reference model",
                  "Within-study\npooled sample SD model",
                  "Weighted internal SD reference"), 2)),
         model = c(rep("Vague priors", 5),
                   "Priors 5",
                   rep("Priors 2", 4),
                   rep("Priors 3", 4),
                   rep("Priors 4", 4))) %>%
  mutate(Estimate = case_when(
    type == "Pooled MD" ~ Estimate,
    type == "External SD reference model" ~ Estimate * external_sd.bi,
    type == "Internal SD reference model" ~ Estimate * internal_sd.bi,
    type == "Within-study\npooled sample SD model" ~ Estimate * internal_sd.bi,
    type == "Weighted internal SD reference" ~ Estimate * weighted_sd.bi 
  )) %>%
  mutate(Q2.5 = case_when(
    type == "Pooled MD" ~ Q2.5,
    type == "External SD reference model" ~ Q2.5 * external_sd.bi,
    type == "Internal SD reference model" ~ Q2.5 * internal_sd.bi,
    type == "Within-study\npooled sample SD model" ~ Q2.5 * internal_sd.bi,
    type == "Weighted internal SD reference" ~ Q2.5 * weighted_sd.bi
  )) %>%
  mutate(Q97.5 = case_when(
    type == "Pooled MD" ~ Q97.5,
    type == "External SD reference model" ~ Q97.5 * external_sd.bi,
    type == "Internal SD reference model" ~ Q97.5 * internal_sd.bi,
    type == "Within-study\npooled sample SD model" ~ Q97.5 * internal_sd.bi,
    type == "Weighted internal SD reference" ~ Q97.5 * weighted_sd.bi
  )) %>%
  mutate_if(is.numeric, round, 2)


# smd between-study SD
# new plot
nice_plot.7 <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = smd_data.final.bi %>%
         mutate(model = factor(model, levels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors")),
                type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")))) +
  stat_interval(aes(group = model, col = model), position = position_dodge(0.75)) +
  geom_point(data = het.numerical.data.bi %>%
               mutate(type = factor(type, levels = c("Pooled MD",
                                                     "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")),
                      model = factor(model, levels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"),
                               labels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"))), aes(Estimate, group = model), size = 3,
             position = position_dodge(0.75)) +
  labs(y = "",
       x = expression(paste(tau)),
       title = "Between-study SD") +
  scale_x_continuous(limits = c(0, 1.25),
                     breaks = seq(-1, 2.5, .25)) +
  scale_color_nejm(breaks = c("Vague priors",
                                                 "Priors 2",
                                                 "Priors 3",
                                                 "Priors 4",
                                                 "Priors 5")) +
  labs(col = "Prior distributions") +
  theme_bw()

# back-conversion visualization
# new plot
nice_plot.8 <- ggplot(aes(x = tau, y = relevel(factor(type), "Pooled MD", after = Inf)), data = md_data_final.bi %>%
         mutate(model = factor(model, levels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors")),
                type = factor(type, levels = c("Pooled MD",
                                               "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")))) +
  stat_interval(aes(group = model, col = model), position = position_dodge(0.75)) +
  geom_point(data = het.numerical.data.rescaled.bi %>%
               mutate(type = factor(type, levels = c("Pooled MD",
                                                     "Weighted internal SD reference",
                                               "External SD reference model",
                                               "Internal SD reference model",
                                               "Within-study\npooled sample SD model"),
                              labels = c("Pooled MD",
                                         "Method 4",
                                         "Method 3",
                                         "Method 2",
                                         "Method 1")),
                      model = factor(model, levels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"),
                               labels = c("Priors 5",
                                                 "Priors 4",
                                                 "Priors 3",
                                                 "Priors 2",
                                                 "Vague priors"))), aes(Estimate, group = model), size = 3,
             position = position_dodge(0.75)) +
  labs(y = "",
       x = expression(paste(tau)),
       title = "Between-study SD (MD estimates)") +
  scale_x_continuous(breaks = seq(-1, 20, 1)) +
  scale_color_nejm(breaks = c("Vague priors",
                                                 "Priors 2",
                                                 "Priors 3",
                                                 "Priors 4",
                                                 "Priors 5")) +
  labs(col = "Prior distributions") +
  theme_bw()


# combining plots
het.plot.bi <- plot_sppb_het.smd.bi + plot_sppb_het.bi


# plot!
ggpubr::ggarrange(nice_plot.5, nice_plot.6, nice_plot.7, nice_plot.8, 
                  nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom")
```


### Visualization of the contribution of each data point to the calculation of internal SD references

We calculated the weights of each study in the meta-analysis and we plotted them against the pooled SDs.

```{r}
### SPPB data
# weights calculation
sppb_data <- sppb_data %>%
  mutate(weights = 1 / se_diff ^ 2)

# plot
sppb_data %>%
  ggplot(aes(x = pre_sd_pooled, y = weights)) +
  geom_vline(xintercept = sppb_internal_sd, col = "blue", size = 1, linetype = 2) +
  geom_vline(xintercept = sppb_weighted_ref, col = "orange", size = 1, linetype = 2) +
  geom_point(aes(size = weights)) +
  ggrepel::geom_label_repel(aes(label = studyID)) +
  labs(x = "Calculated pooled SD",
       y = "Meta-analysis weights") +
  theme_tidybayes() +
  panel_border() +
  scale_x_continuous(breaks = c(1.5, sppb_weighted_ref, 1.75, 2, 2.25, sppb_internal_sd, 2.5, 2.75),
                     labels = c(1.5, "Weighted\ninternal SD reference", 1.75, 2, 2.25, "NICE\n internal SD reference", 2.5, 2.75)) +
  theme(legend.position = "none")


### BI data
# weights calculation
bi_data <- bi_data %>%
  mutate(weights = 1 / se_diff ^ 2)

# plot
bi_data %>%
  ggplot(aes(x = pre_sd_pooled, y = weights)) +
  geom_vline(xintercept = internal_sd.bi, col = "blue", size = 1, linetype = 2) +
  geom_vline(xintercept = weighted.mean(bi_data$pre_sd_pooled, bi_data$weights), col = "orange", size = 1, linetype = 2) +
  geom_point(aes(size = weights)) +
  ggrepel::geom_label_repel(aes(label = studyID)) +
  labs(x = "Calculated pooled SD",
       y = "Meta-analysis weights") +
  theme_tidybayes() +
  panel_border() +
  scale_x_continuous(breaks = c(10, 12, weighted.mean(bi_data$pre_sd_pooled, bi_data$weights), internal_sd.bi, 18, 20, 22, 24),
                     labels = c(10, 12, "Weighted\ninternal\nSD reference", "NICE internal\nSD reference", 18, 20, 22, 24)) +
  theme(legend.position = "none")
```


### Sensitivity analysis: Frequentist approach

```{r}
## SPPB data
# Mean differences
m.gen.sppb.DL.MD <- metagen(TE = diff, 
                 seTE = se_diff, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "MD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", # DerSimonian-Laird estimator
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.sppb.DL.MD)
m.gen.sppb.REML.MD <- metagen(TE = diff, 
                 seTE = se_diff, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "MD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", # Restricted Maximum Likelihood estimator
                 hakn = TRUE, 
                 title = "Meta-methodological work")

# SMDs using an external SD reference
m.gen.sppb.DL.ext <- metagen(TE = diff_ext, 
                 seTE = se_diff_ext, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.sppb.DL.ext)
m.gen.sppb.REML.ext <- metagen(TE = diff_ext, 
                 seTE = se_diff_ext, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")

# SMDs using a calculated pooled internal SD reference
m.gen.sppb.DL.int <- metagen(TE = diff_int, 
                 seTE = se_diff_int, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.sppb.DL.int)
m.gen.sppb.REML.int <- metagen(TE = diff_int, 
                 seTE = se_diff_int, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")

# SMDs using an internal SD reference at baseline
m.gen.sppb.DL.pre <- metagen(TE = diff_pre, 
                 seTE = se_diff_pre, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.sppb.DL.pre)
m.gen.sppb.REML.pre <- metagen(TE = diff_pre, 
                 seTE = se_diff_pre, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")

# SMDs using an internal SD reference at post-intervention
m.gen.sppb.DL.post <- metagen(TE = diff_post, 
                 seTE = se_diff_post, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.sppb.DL.post)
m.gen.sppb.REML.post <- metagen(TE = diff_post, 
                 seTE = se_diff_post, 
                 studlab = studyID, 
                 data = sppb_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")

sppb.metadata <- data.frame(model = rep(c("Study-specific pooled SD\n(at post-intervention)",
                         "Study-specific pooled SD\n(at pre-intervention)",
                         "Internal SD",
                         "External SD"), times = 2),
           estimator = rep(c("DerSimonian-Laird",
                             "Restricted Maximum Likelihood"), each = 4),
           estimate = c(m.gen.sppb.DL.post$TE.random,
                        m.gen.sppb.DL.pre$TE.random,
                        m.gen.sppb.DL.int$TE.random,
                        m.gen.sppb.DL.ext$TE.random,
                        m.gen.sppb.REML.post$TE.random,
                        m.gen.sppb.REML.pre$TE.random,
                        m.gen.sppb.REML.int$TE.random,
                        m.gen.sppb.REML.ext$TE.random),
           lower = c(m.gen.sppb.DL.post$lower.random,
                        m.gen.sppb.DL.pre$lower.random,
                        m.gen.sppb.DL.int$lower.random,
                        m.gen.sppb.DL.ext$lower.random,
                        m.gen.sppb.REML.post$lower.random,
                        m.gen.sppb.REML.pre$lower.random,
                        m.gen.sppb.REML.int$lower.random,
                        m.gen.sppb.REML.ext$lower.random),
           upper = c(m.gen.sppb.DL.post$upper.random,
                        m.gen.sppb.DL.pre$upper.random,
                        m.gen.sppb.DL.int$upper.random,
                        m.gen.sppb.DL.ext$upper.random,
                        m.gen.sppb.REML.post$upper.random,
                        m.gen.sppb.REML.pre$upper.random,
                        m.gen.sppb.REML.int$upper.random,
                        m.gen.sppb.REML.ext$upper.random),
           tau = c(m.gen.sppb.DL.post$tau,
                        m.gen.sppb.DL.pre$tau,
                        m.gen.sppb.DL.int$tau,
                        m.gen.sppb.DL.ext$tau,
                        m.gen.sppb.REML.post$tau,
                        m.gen.sppb.REML.pre$tau,
                        m.gen.sppb.REML.int$tau,
                        m.gen.sppb.REML.ext$tau),
           lower.tau = c(m.gen.sppb.DL.post$lower.tau,
                        m.gen.sppb.DL.pre$lower.tau,
                        m.gen.sppb.DL.int$lower.tau,
                        m.gen.sppb.DL.ext$lower.tau,
                        m.gen.sppb.REML.post$lower.tau,
                        m.gen.sppb.REML.pre$lower.tau,
                        m.gen.sppb.REML.int$lower.tau,
                        m.gen.sppb.REML.ext$lower.tau),
           upper.tau = c(m.gen.sppb.DL.post$upper.tau,
                        m.gen.sppb.DL.pre$upper.tau,
                        m.gen.sppb.DL.int$upper.tau,
                        m.gen.sppb.DL.ext$upper.tau,
                        m.gen.sppb.REML.post$upper.tau,
                        m.gen.sppb.REML.pre$upper.tau,
                        m.gen.sppb.REML.int$upper.tau,
                        m.gen.sppb.REML.ext$upper.tau))

# plot
## relative effect estimates
tiff("effects_freq.tiff", width = 9, height = 7, res = 300, units = "in")
sppb.metadata %>%
  ggplot(aes(x = estimate, y = model, group = estimator, col = estimator)) +
  geom_pointrange(aes(xmin = lower,
                      xmax = upper),
                  position = position_dodge(width = 0.5)) +
  geom_vline(xintercept = 0, linetype = 2) +
  labs(x = "Relative effect estimates (SMD)",
       y = element_blank(),
       col = "Between-study heterogeneity estimator") +
  theme_bw() +
  scale_color_lancet() +
  theme(legend.position = "bottom")
dev.off()

## between-study heterogeneity (tau; SD)
tiff("sppb_tau_freq.tiff", width = 9, height = 7, res = 300, units = "in")
sppb.metadata %>%
  ggplot(aes(x = tau, y = model, group = estimator, col = estimator)) +
  geom_pointrange(aes(xmin = lower.tau,
                      xmax = upper.tau),
                  position = position_dodge(width = 0.5)) +
  labs(x = expression(paste(tau, " estimates (SMD)")),
       y = element_blank(),
       col = "Between-study heterogeneity estimator") +
  theme_bw() +
  scale_color_lancet() +
  theme(legend.position = "bottom")
dev.off()


## Barthel Index data
# Mean differences
m.gen.bi.DL.MD <- metagen(TE = diff, 
                 seTE = se_diff, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "MD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.bi.DL.MD)
m.gen.bi.REML.MD <- metagen(TE = diff, 
                 seTE = se_diff, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "MD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")

# SMDs using an external SD reference
m.gen.bi.DL.ext <- metagen(TE = diff_ext, 
                 seTE = se_diff_ext, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.bi.DL.ext)
m.gen.bi.REML.ext <- metagen(TE = diff_ext, 
                 seTE = se_diff_ext, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")

# SMDs using a calculated pooled internal SD reference
m.gen.bi.DL.int <- metagen(TE = diff_int, 
                 seTE = se_diff_int, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.bi.DL.int)
m.gen.bi.REML.int <- metagen(TE = diff_int, 
                 seTE = se_diff_int, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")

# SMDs using an internal SD reference at baseline
m.gen.bi.DL.pre <- metagen(TE = diff_pre, 
                 seTE = se_diff_pre, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.bi.DL.pre)
m.gen.bi.REML.pre <- metagen(TE = diff_pre, 
                 seTE = se_diff_pre, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")

# SMDs using an internal SD reference at post-intervention
m.gen.bi.DL.post <- metagen(TE = diff_post, 
                 seTE = se_diff_post, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "DL", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")
summary(m.gen.bi.DL.post)
m.gen.bi.REML.post <- metagen(TE = diff_post, 
                 seTE = se_diff_post, 
                 studlab = studyID, 
                 data = bi_data, 
                 sm = "SMD", 
                 fixed = FALSE, 
                 random = TRUE,
                 method.tau = "REML", 
                 hakn = TRUE, 
                 title = "Meta-methodological work")

# Data storage
bi.metadata <- data.frame(model = rep(c("Study-specific pooled SD\n(at post-intervention)",
                         "Study-specific pooled SD\n(at pre-intervention)",
                         "Internal SD",
                         "External SD"), times = 2),
           estimator = rep(c("DerSimonian-Laird",
                             "Restricted Maximum Likelihood"), each = 4),
           estimate = c(m.gen.bi.DL.post$TE.random,
                        m.gen.bi.DL.pre$TE.random,
                        m.gen.bi.DL.int$TE.random,
                        m.gen.bi.DL.ext$TE.random,
                        m.gen.bi.REML.post$TE.random,
                        m.gen.bi.REML.pre$TE.random,
                        m.gen.bi.REML.int$TE.random,
                        m.gen.bi.REML.ext$TE.random),
           lower = c(m.gen.bi.DL.post$lower.random,
                        m.gen.bi.DL.pre$lower.random,
                        m.gen.bi.DL.int$lower.random,
                        m.gen.bi.DL.ext$lower.random,
                        m.gen.bi.REML.post$lower.random,
                        m.gen.bi.REML.pre$lower.random,
                        m.gen.bi.REML.int$lower.random,
                        m.gen.bi.REML.ext$lower.random),
           upper = c(m.gen.bi.DL.post$upper.random,
                        m.gen.bi.DL.pre$upper.random,
                        m.gen.bi.DL.int$upper.random,
                        m.gen.bi.DL.ext$upper.random,
                        m.gen.bi.REML.post$upper.random,
                        m.gen.bi.REML.pre$upper.random,
                        m.gen.bi.REML.int$upper.random,
                        m.gen.bi.REML.ext$upper.random),
           tau = c(m.gen.bi.DL.post$tau,
                        m.gen.bi.DL.pre$tau,
                        m.gen.bi.DL.int$tau,
                        m.gen.bi.DL.ext$tau,
                        m.gen.bi.REML.post$tau,
                        m.gen.bi.REML.pre$tau,
                        m.gen.bi.REML.int$tau,
                        m.gen.bi.REML.ext$tau),
           lower.tau = c(m.gen.bi.DL.post$lower.tau,
                        m.gen.bi.DL.pre$lower.tau,
                        m.gen.bi.DL.int$lower.tau,
                        m.gen.bi.DL.ext$lower.tau,
                        m.gen.bi.REML.post$lower.tau,
                        m.gen.bi.REML.pre$lower.tau,
                        m.gen.bi.REML.int$lower.tau,
                        m.gen.bi.REML.ext$lower.tau),
           upper.tau = c(m.gen.bi.DL.post$upper.tau,
                        m.gen.bi.DL.pre$upper.tau,
                        m.gen.bi.DL.int$upper.tau,
                        m.gen.bi.DL.ext$upper.tau,
                        m.gen.bi.REML.post$upper.tau,
                        m.gen.bi.REML.pre$upper.tau,
                        m.gen.bi.REML.int$upper.tau,
                        m.gen.bi.REML.ext$upper.tau))

# plot
## relative effect estimates
bi.metadata %>%
  ggplot(aes(x = estimate, y = model, group = estimator, col = estimator)) +
  geom_pointrange(aes(xmin = lower,
                      xmax = upper),
                  position = position_dodge(width = 0.5)) +
  geom_vline(xintercept = 0, linetype = 2) +
  labs(x = "Relative effect estimates (SMD)",
       y = element_blank(),
       col = "Between-study heterogeneity estimator") +
  theme_bw() +
  scale_color_lancet() +
  theme(legend.position = "bottom")

## between-study heterogeneity (tau; SD)
bi.metadata %>%
  ggplot(aes(x = tau, y = model, group = estimator, col = estimator)) +
  geom_pointrange(aes(xmin = lower.tau,
                      xmax = upper.tau),
                  position = position_dodge(width = 0.5)) +
  labs(x = expression(paste(tau, " estimates (SMD)")),
       y = element_blank(),
       col = "Between-study heterogeneity estimator") +
  theme_bw() +
  scale_color_lancet() +
  theme(legend.position = "bottom")


### Re-expression methods

## SPPB
## Method 1: using the same SD reference for standardization
# adding "Pooled MD" results
sppb.metadata[9, ] <- c("Pooled MD", "DerSimonian-Laird", m.gen.sppb.DL.MD$TE.random, m.gen.sppb.DL.MD$lower.random, m.gen.sppb.DL.MD$upper.random, m.gen.sppb.DL.MD$tau,
                        m.gen.sppb.DL.MD$lower.tau, m.gen.sppb.DL.MD$upper.tau)
sppb.metadata[10, ] <- c("Pooled MD", "Restricted Maximum Likelihood", m.gen.sppb.REML.MD$TE.random, m.gen.sppb.REML.MD$lower.random, m.gen.sppb.REML.MD$upper.random, m.gen.sppb.REML.MD$tau,
                        m.gen.sppb.REML.MD$lower.tau, m.gen.sppb.REML.MD$upper.tau)


# re-expressing meta-analysis results
sppb.metadata <- sppb.metadata %>%
  mutate(estimate = as.numeric(estimate),
         lower = as.numeric(lower),
         upper = as.numeric(upper),
         tau = as.numeric(tau),
         lower.tau = as.numeric(lower.tau),
         upper.tau = as.numeric(upper.tau)) %>%
  # re-expressing SMD estimates
  mutate(estimate_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ estimate * sppb_external_sd,
    model == "Internal SD" ~ estimate * sppb_external_sd,
    model == "External SD" ~ estimate * sppb_external_sd,
    model == "Pooled MD" ~ estimate),
    # re-expressing lower bounds
    lower_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ lower * sppb_external_sd,
    model == "Internal SD" ~ lower * sppb_external_sd,
    model == "External SD" ~ lower * sppb_external_sd,
    model == "Pooled MD" ~ lower),
    # re-expressing upper bounds
    upper_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ upper * sppb_external_sd,
    model == "Internal SD" ~ upper * sppb_external_sd,
    model == "External SD" ~ upper * sppb_external_sd,
    model == "Pooled MD" ~ upper),
    # re-expressing tau estimates
    tau_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ tau * sppb_external_sd,
    model == "Internal SD" ~ tau * sppb_external_sd,
    model == "External SD" ~ tau * sppb_external_sd,
    model == "Pooled MD" ~ tau),
    # re-expressing tau lower bounds
    lower.tau_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ lower.tau * sppb_external_sd,
    model == "Internal SD" ~ lower.tau * sppb_external_sd,
    model == "External SD" ~ lower.tau * sppb_external_sd,
    model == "Pooled MD" ~ lower.tau),
    # re-expressing tau upper bounds
    upper.tau_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ upper.tau * sppb_external_sd,
    model == "Internal SD" ~ upper.tau * sppb_external_sd,
    model == "External SD" ~ upper.tau * sppb_external_sd,
    model == "Pooled MD" ~ upper.tau))


# plotting
## relative effect estimates
plot.1 <- sppb.metadata %>%
  mutate(model = factor(model,
                        levels = c("Pooled MD",
                                   "External SD",
                                   "Internal SD",
                                   "Study-specific pooled SD\n(at pre-intervention)",
                                   "Study-specific pooled SD\n(at post-intervention)"))) %>%
  ggplot(aes(x = estimate_re, y = model, group = estimator, col = estimator)) +
  geom_pointrange(aes(xmin = lower_re,
                      xmax = upper_re),
                  position = position_dodge(width = 0.5)) +
  geom_vline(xintercept = 0, linetype = 2) +
  labs(x = "Relative effect estimates (MD)",
       y = element_blank(),
       col = "Between-study heterogeneity estimator") +
  theme_bw() +
  scale_color_lancet() +
  theme(legend.position = "bottom")

## tau estimates
plot.2 <- sppb.metadata %>%
  mutate(model = factor(model,
                        levels = c("Pooled MD",
                                   "External SD",
                                   "Internal SD",
                                   "Study-specific pooled SD\n(at pre-intervention)",
                                   "Study-specific pooled SD\n(at post-intervention)"))) %>%
  ggplot(aes(x = tau_re, y = model, group = estimator, col = estimator)) +
  geom_pointrange(aes(xmin = lower.tau_re,
                      xmax = upper.tau_re),
                  position = position_dodge(width = 0.5)) +
  labs(x = expression(paste(tau, " estimates (MD)")),
       y = element_blank(),
       col = "Between-study heterogeneity estimator") +
  theme_bw() +
  scale_color_lancet() +
  theme(legend.position = "bottom")

# combining plots
ggpubr::ggarrange(plot.1, plot.2, 
                  ncol = 1, 
                  common.legend = TRUE,
                  legend = "bottom")



## Barthel Index
## Method 1: using the same SD reference for standardization
# adding "Pooled MD" results
bi.metadata[9, ] <- c("Pooled MD", "DerSimonian-Laird", m.gen.bi.DL.MD$TE.random, m.gen.bi.DL.MD$lower.random, m.gen.bi.DL.MD$upper.random, m.gen.bi.DL.MD$tau,
                        m.gen.bi.DL.MD$lower.tau, m.gen.bi.DL.MD$upper.tau)
bi.metadata[10, ] <- c("Pooled MD", "Restricted Maximum Likelihood", m.gen.bi.REML.MD$TE.random, m.gen.bi.REML.MD$lower.random, m.gen.bi.REML.MD$upper.random, m.gen.bi.REML.MD$tau,
                        m.gen.bi.REML.MD$lower.tau, m.gen.bi.REML.MD$upper.tau)


# re-expressing meta-analysis results
bi.metadata <- bi.metadata %>%
  mutate(estimate = as.numeric(estimate),
         lower = as.numeric(lower),
         upper = as.numeric(upper),
         tau = as.numeric(tau),
         lower.tau = as.numeric(lower.tau),
         upper.tau = as.numeric(upper.tau)) %>%
  # re-expressing SMD estimates
  mutate(estimate_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ estimate * external_sd.bi,
    model == "Internal SD" ~ estimate * external_sd.bi,
    model == "External SD" ~ estimate * external_sd.bi,
    model == "Pooled MD" ~ estimate),
    # re-expressing lower bounds
    lower_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ lower * external_sd.bi,
    model == "Internal SD" ~ lower * external_sd.bi,
    model == "External SD" ~ lower * external_sd.bi,
    model == "Pooled MD" ~ lower),
    # re-expressing upper bounds
    upper_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ upper * external_sd.bi,
    model == "Internal SD" ~ upper * external_sd.bi,
    model == "External SD" ~ upper * external_sd.bi,
    model == "Pooled MD" ~ upper),
    # re-expressing tau estimates
    tau_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ tau * external_sd.bi,
    model == "Internal SD" ~ tau * external_sd.bi,
    model == "External SD" ~ tau * external_sd.bi,
    model == "Pooled MD" ~ tau),
    # re-expressing tau lower bounds
    lower.tau_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ lower.tau * external_sd.bi,
    model == "Internal SD" ~ lower.tau * external_sd.bi,
    model == "External SD" ~ lower.tau * external_sd.bi,
    model == "Pooled MD" ~ lower.tau),
    # re-expressing tau upper bounds
    upper.tau_re = case_when(
    model %in% c("Study-specific pooled SD\n(at pre-intervention)",
                 "Study-specific pooled SD\n(at post-intervention)") ~ upper.tau * external_sd.bi,
    model == "Internal SD" ~ upper.tau * external_sd.bi,
    model == "External SD" ~ upper.tau * external_sd.bi,
    model == "Pooled MD" ~ upper.tau))


# plotting
## relative effect estimates
plot.1 <- bi.metadata %>%
  mutate(model = factor(model,
                        levels = c("Pooled MD",
                                   "External SD",
                                   "Internal SD",
                                   "Study-specific pooled SD\n(at pre-intervention)",
                                   "Study-specific pooled SD\n(at post-intervention)"))) %>%
  ggplot(aes(x = estimate_re, y = model, group = estimator, col = estimator)) +
  geom_pointrange(aes(xmin = lower_re,
                      xmax = upper_re),
                  position = position_dodge(width = 0.5)) +
  geom_vline(xintercept = 0, linetype = 2) +
  labs(x = "Relative effect estimates (MD)",
       y = element_blank(),
       col = "Between-study heterogeneity estimator") +
  theme_bw() +
  scale_color_lancet() +
  theme(legend.position = "bottom")

## tau estimates
plot.2 <- bi.metadata %>%
  mutate(model = factor(model,
                        levels = c("Pooled MD",
                                   "External SD",
                                   "Internal SD",
                                   "Study-specific pooled SD\n(at pre-intervention)",
                                   "Study-specific pooled SD\n(at post-intervention)"))) %>%
  ggplot(aes(x = tau_re, y = model, group = estimator, col = estimator)) +
  geom_pointrange(aes(xmin = lower.tau_re,
                      xmax = upper.tau_re),
                  position = position_dodge(width = 0.5)) +
  labs(x = expression(paste(tau, " estimates (MD)")),
       y = element_blank(),
       col = "Between-study heterogeneity estimator") +
  theme_bw() +
  scale_color_lancet() +
  theme(legend.position = "bottom")
```

```{r}
sessionInfo()
```

